Simulation

### 2018-12-13 _analyze.Rmd
Update lib_dir

---
title: '`r paste("Experiment", params$experiment)`'
description: |
  Data analysis for Experiment `r params$experiment`.
author:
  - name: Matti Vuorre 
    affiliation: Columbia University
date: "`r Sys.Date()`"
output: 
  radix::radix_article:
    toc: true
    toc_depth: 2
    self_contained: false
    lib_dir: "docs/site_libs"
params:
  experiment: 3
---

>>>>

---
title: '`r paste("Experiment", params$experiment)`'
description: |
  Data analysis for Experiment `r params$experiment`.
author:
  - name: Matti Vuorre 
    affiliation: Columbia University
date: "`r Sys.Date()`"
output: 
  radix::radix_article:
    toc: true
    toc_depth: 2
    self_contained: false
params:
  experiment: 3
---

### 2018-12-13 index.Rmd
I guess I'm using packrat now
Revert "Add sessioninfo"
This reverts commit cfe495132a2ee3623946af2317d55df78f972608.
Small updates to language and formatting
Update lib_dir

---
title: "Math Metacognition"
description: |
  Analyses of math metacognition data
date: "`r Sys.Date()`"
author:
  - name: Matti Vuorre 
    affiliation: Columbia University
output: 
  radix::radix_article:
    toc: true
    toc_depth: 1
    self_contained: false
    lib_dir: "site_libs"
site: radix::radix_website
---

@@

```{r, eval = T}
dat <- read_csv("data/merged.csv", guess_max = 25000)
dat
```

@@

# Session information

```{r sessioninfo, layout="l-body-outset"}
options(width=140)
library(sessioninfo)
session_info()
options(width=125)
```

>>>>

---
title: "Math Metacognition"
description: |
  Analyses of math metacognition data
date: "`r Sys.Date()`"
author:
  - name: Matti Vuorre 
    affiliation: Columbia University
output: 
  radix::radix_article:
    toc: true
    toc_depth: 1
    self_contained: false
site: radix::radix_website
---

@@

```{r, eval = T}
dat <- read_csv("data/merged.csv", guess_max = 25000)
head(dat) %>% kable()
```

@@

### 2018-12-13 simulation.Rmd
Update lib_dir

---
title: "Simulation"
description: |
  A simulation study investigating the impact of task knowledge and guessing on resolution metrics
author:
  - name: Matti Vuorre 
    affiliation: Columbia University
date: "`r Sys.Date()`"
output: 
  radix::radix_article:
    toc: true
    toc_depth: 2
    self_contained: false
    lib_dir: "site_libs"
bibliography: bibliography.bib
---

>>>>

---
title: "Simulation"
description: |
  A simulation study investigating the impact of task knowledge and guessing on resolution metrics
author:
  - name: Matti Vuorre 
    affiliation: Columbia University
date: "`r Sys.Date()`"
output: 
  radix::radix_article:
    toc: true
    toc_depth: 2
    self_contained: false
bibliography: bibliography.bib
---
